Synpotic Soil Characterization

### 2025-08-13 3-reports/manuscript_figures.Rmd
update elevation script

gg_wle = 
  elevation_processed %>% 
  filter(region == "Erie") %>% 
  ggplot(aes(x = distance_to_water_m, y = elev_m, color = transect))+
  geom_line(color = "black")+
  geom_point(size = 4)+
  scale_color_manual(values = c("grey", "#2E5894", "#FFB200", "#96001B"),
                     breaks = c("water edge", "wetland", "transition", "upland"))+
  facet_nested_wrap(region ~ site)+
  labs(x = "",
       y = "Elevation, m
       ",
       color = "")+
#  theme(legend.position = c(0.1,0.61))+
  NULL

>>>>

gg_wle = 
  elevation_processed %>% 
  filter(region == "Erie") %>% 
  ggplot(aes(x = distance_to_water_m, y = elev_m, color = transect, linetype = site))+
  geom_line(color = "black", show.legend = F)+
  geom_point(size = 4)+
  scale_color_manual(values = c("grey", "#2E5894", "#FFB200", "#96001B"),
                     breaks = c("water edge", "wetland", "transition", "upland"))+
  scale_linetype_manual(values = c("dashed", "solid", "solid"),
                     breaks = c("CRC", "PTR", "OWC"))+
  facet_nested_wrap(region ~ site)+
  labs(x = "",
       y = "Elevation, m
       ",
       color = "")+
#  theme(legend.position = c(0.1,0.61))+
  NULL
